---
title: "Another estimator of Kendall's tau"
author: "YI-CHENG, TAI"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(mvtnorm)
library(survival)
```

There are continuous random variables $(T, X_2)$, where $T$ is subject to censoring, $C$. <br>
```{r}
set.seed(20200614)
C.rate <- 0.07
## generate (Y, delta, X), where X is binary and Y is lifetime with censoring
size <- 200
rho <- -0.55
corr.matrix <- matrix(c(1, rho, rho, 1), nrow = 2)
Z <- rmvnorm(n = size, mean = c(0, 0), sigma = corr.matrix)
T1 <- exp(Z[, 1])
X2 <- Z[, 2]
C <- rexp(n = size, rate = C.rate)
Y1 <- ifelse(T1 < C, T1, C)
delta <- ifelse(T1 < C, 1, 0)
```

#### Kaplan-Meier estimate of the censoring, $C$
```{r}
G.fit <- survfit(Surv(time = Y1, event = 1 - delta) ~ 1)
G_func <- stepfun(x = G.fit$time, y = c(1, G.fit$surv))
```

#### True Value of concordance and discordance
```{r}
df.pair <- matrix(nrow = choose(n = size, k = 2), ncol = 8)
k <- 1
for(i in seq(1, size - 1)) {
  for(j in seq(i + 1, size)) {
    df.pair[k, ] <- c(X2[i], Y1[i], delta[i], T1[i], X2[j], Y1[j], delta[j], T1[j])
    k <- k + 1
  }
}

c1 <- mean(df.pair[, 4] > df.pair[, 8] & df.pair[, 1] > df.pair[, 5])
c2 <- mean(df.pair[, 4] < df.pair[, 8] & df.pair[, 1] < df.pair[, 5])
c1 + c2 ## concordance

d1 <- mean(df.pair[, 4] > df.pair[, 8] & df.pair[, 1] < df.pair[, 5])
d2 <- mean(df.pair[, 4] < df.pair[, 8] & df.pair[, 1] > df.pair[, 5])
d1 + d2 ## discordance
```

#### Estimate for concordance with known $G$
```{r}
G.ip <- 1 - pexp(q = df.pair[, 6], rate = C.rate)
G.i <- 1 - pexp(q = df.pair[, 2], rate = C.rate)

# sum(G.ip == 0)
# sum(G.i == 0)

c1.h <- (df.pair[, 2] > df.pair[, 6] & df.pair[, 7] == 1 & df.pair[, 1] > df.pair[, 5]) / (G.ip ^ 2)
c2.h <- (df.pair[, 2] < df.pair[, 6] & df.pair[, 3] == 1 & df.pair[, 1] < df.pair[, 5]) / (G.i ^ 2)
mean(c1.h + c2.h)
```

#### Estimate for discordance with known $G$
```{r}
d1.h <- (df.pair[, 2] > df.pair[, 6] & df.pair[, 7] == 1 & df.pair[, 1] < df.pair[, 5]) / (G.ip ^ 2)
d2.h <- (df.pair[, 2] < df.pair[, 6] & df.pair[, 3] == 1 & df.pair[, 1] > df.pair[, 5]) / (G.i ^ 2)
mean(d1.h + d2.h)
```

#### Estimate for concordance with estimated $G$
```{r}
G.ip <- G_func(df.pair[, 6])
G.i <- G_func(df.pair[, 2])

# sum(G.ip == 0)
# sum(G.i == 0)

c1.h <- (df.pair[, 2] > df.pair[, 6] & df.pair[, 7] == 1 & df.pair[, 1] > df.pair[, 5]) / (G.ip ^ 2)
c2.h <- (df.pair[, 2] < df.pair[, 6] & df.pair[, 3] == 1 & df.pair[, 1] < df.pair[, 5]) / (G.i ^ 2)
mean(c1.h + c2.h)
```

#### Estimate for discordance with estimated $G$
```{r}
d1.h <- (df.pair[, 2] > df.pair[, 6] & df.pair[, 7] == 1 & df.pair[, 1] < df.pair[, 5]) / (G.ip ^ 2)
d2.h <- (df.pair[, 2] < df.pair[, 6] & df.pair[, 3] == 1 & df.pair[, 1] > df.pair[, 5]) / (G.i ^ 2)
mean(d1.h + d2.h)
```

#### Monte-Carlo Simulation
rho.seq = c(-0.7, -0.45, 0, 0.45, 0.7)
rate.seq = c(0.07, 0.28, 0.65, 1.4, 4)
```{r}
set.seed(20200614)
C.rate <- 4
size <- 200
rho <- 0.7
corr.matrix <- matrix(c(1, rho, rho, 1), nrow = 2)

sim <- replicate(n = 500, expr = {
  ## generate (Y, delta, X), where X is continuous and Y is lifetime with censoring
  Z <- rmvnorm(n = size, mean = c(0, 0), sigma = corr.matrix)
  T1 <- exp(Z[, 1])
  X2 <- Z[, 2]
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  
  df.pair <- matrix(nrow = choose(n = size, k = 2), ncol = 8)
  k <- 1
  for(i in seq(1, size - 1)) {
    for(j in seq(i + 1, size)) {
      df.pair[k, ] <- c(X2[i], Y1[i], delta[i], T1[i], X2[j], Y1[j], delta[j], T1[j])
      k <- k + 1
    }
  }
  
  ## K-M of Censoring
  G.fit <- survfit(Surv(time = Y1, event = 1 - delta) ~ 1)
  G_func <- stepfun(x = G.fit$time, y = c(1, G.fit$surv))
  
  ## true concordance
  c1 <- mean(df.pair[, 4] > df.pair[, 8] & df.pair[, 1] > df.pair[, 5])
  c2 <- mean(df.pair[, 4] < df.pair[, 8] & df.pair[, 1] < df.pair[, 5])
  c.true <- c1 + c2 
  
  ## true discordance
  d1 <- mean(df.pair[, 4] > df.pair[, 8] & df.pair[, 1] < df.pair[, 5])
  d2 <- mean(df.pair[, 4] < df.pair[, 8] & df.pair[, 1] > df.pair[, 5])
  d.true <- d1 + d2
  
  ## true denominator
  G.ip <- 1 - pexp(q = df.pair[, 6], rate = C.rate)
  G.i <- 1 - pexp(q = df.pair[, 2], rate = C.rate)
  
  ## estimate of c with known G
  c1.t <- (df.pair[, 2] > df.pair[, 6] & df.pair[, 7] == 1 & df.pair[, 1] > df.pair[, 5]) / (G.ip ^ 2)
  c2.t <- (df.pair[, 2] < df.pair[, 6] & df.pair[, 3] == 1 & df.pair[, 1] < df.pair[, 5]) / (G.i ^ 2)
  c.tilde <- mean(c1.t + c2.t)
  
  ## estimate of d with known G
  d1.t <- (df.pair[, 2] > df.pair[, 6] & df.pair[, 7] == 1 & df.pair[, 1] < df.pair[, 5]) / (G.ip ^ 2)
  d2.t <- (df.pair[, 2] < df.pair[, 6] & df.pair[, 3] == 1 & df.pair[, 1] > df.pair[, 5]) / (G.i ^ 2)
  d.tilde <- mean(d1.t + d2.t)
  
  ## estimated denominator
  G.ip <- G_func(df.pair[, 6])
  G.i <- G_func(df.pair[, 2])
  
  ## estimate of c with estimated G
  c1.h <- (df.pair[, 2] > df.pair[, 6] & df.pair[, 7] == 1 & df.pair[, 1] > df.pair[, 5]) / (G.ip ^ 2)
  c2.h <- (df.pair[, 2] < df.pair[, 6] & df.pair[, 3] == 1 & df.pair[, 1] < df.pair[, 5]) / (G.i ^ 2)
  c1.h <- ifelse(G.ip == 0, 0, c1.h)
  c2.h <- ifelse(G.i == 0, 0, c2.h)
  c.hat <- mean(c1.h + c2.h)
  
  ## estimate of d with estimated G
  d1.h <- (df.pair[, 2] > df.pair[, 6] & df.pair[, 7] == 1 & df.pair[, 1] < df.pair[, 5]) / (G.ip ^ 2)
  d2.h <- (df.pair[, 2] < df.pair[, 6] & df.pair[, 3] == 1 & df.pair[, 1] > df.pair[, 5]) / (G.i ^ 2)
  d1.h <- ifelse(G.ip == 0, 0, d1.h)
  d2.h <- ifelse(G.i == 0, 0, d2.h)
  d.hat <- mean(d1.h + d2.h)
  
  
  return(list(c.true = c.true, d.true = d.true,
              c.tilde = c.tilde, d.tilde = d.tilde,
              c.hat = c.hat, d.hat = d.hat,
              c.rate = mean(delta)))
})
```

```{r}
mean(unlist(sim["c.true", ]))
mean(unlist(sim["d.true", ]))

mean(unlist(sim["c.tilde", ]))
mean(unlist(sim["d.tilde", ]))

mean(unlist(sim["c.hat", ]))
mean(unlist(sim["d.hat", ]))


# mean(unlist(sim["c.true", ]) - unlist(sim["d.true", ]))
# mean(unlist(sim["c.rate", ]))
```

```{r}
sd(unlist(sim["c.tilde", ]))
sd(unlist(sim["d.tilde", ]))

sd(unlist(sim["c.hat", ]))
sd(unlist(sim["d.hat", ]))
```

