---
title: "Untitled"
author: "YI-CHENG, TAI"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(survival)
source("GC_imputation_func.R")
```

The case that the distributions of two groups are different but $\tau_{10} = 0$:
```{r}
par(mfrow = c(1, 3))
curve(1 - pweibull(x, shape = 2, scale = 1.22), from = 0, to = 8, xlab = "t", ylab = "survival")
curve(1 - pweibull(x, shape = 0.5, scale = 2), from = 0, to = 8, lty = 2, add = TRUE)
legend("topright", legend = c("k=2, lambda=1.22", "k=0.5, lambda=2"), lty = c(1, 2))

curve(dweibull(x, shape = 2, scale = 1.22), from = 0, to = 5, xlab = "t", ylab = "density",
      ylim = c(0, 1.5))
curve(dweibull(x, shape = 0.5, scale = 2), from = 0, to = 5, lty = 2, add = TRUE)
legend("topright", legend = c("k=2, lambda=1.22", "k=0.5, lambda=2"), lty = c(1, 2))

curve(dweibull(x, shape = 2, scale = 1.22) / (1 - pweibull(x, shape = 2, scale = 1.22)),
      from = 0, to = 3, xlab = "t", ylab = "hazard",
      ylim = c(0, 4))
curve(dweibull(x, shape = 0.5, scale = 2) / (1 - pweibull(x, shape = 0.5, scale = 2)),
      from = 0, to = 3, lty = 2, add = TRUE)
legend("topright", legend = c("k=2, lambda=1.22", "k=0.5, lambda=2"), lty = c(1, 2))
```

```{r}
par(mfrow = c(1, 3))
curve(1 - pweibull(x, shape = 1, scale = 4), from = 0, to = 8, xlab = "t", ylab = "survival")
curve(1 - pweibull(x, shape = 1, scale = 2), from = 0, to = 8, lty = 2, add = TRUE)
legend("topright", legend = c("k=2, lambda=1.22", "k=0.5, lambda=2"), lty = c(1, 2))

curve(dweibull(x, shape = 1, scale = 4), from = 0, to = 5, xlab = "t", ylab = "density",
      ylim = c(0, 1.5))
curve(dweibull(x, shape = 1, scale = 2), from = 0, to = 5, lty = 2, add = TRUE)
legend("topright", legend = c("k=2, lambda=1.22", "k=0.5, lambda=2"), lty = c(1, 2))

curve(dweibull(x, shape = 1, scale = 4) / (1 - pweibull(x, shape = 2, scale = 1.22)),
      from = 0, to = 3, xlab = "t", ylab = "hazard",
      ylim = c(0, 4))
curve(dweibull(x, shape = 1, scale = 2) / (1 - pweibull(x, shape = 0.5, scale = 2)),
      from = 0, to = 3, lty = 2, add = TRUE)
legend("topright", legend = c("k=2, lambda=1.22", "k=0.5, lambda=2"), lty = c(1, 2))
```

**approximate $\tau_{10}$** <br>
Check that $\tau_{10} = 0$ being true.
```{r}
B <- 5000
size <- 2000

sim <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 2, scale = 1.22)
  T12 <- rweibull(n = size, shape = 0.5, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  
  return(list(median1 = median(T11),
              median2 = median(T12),
              tau = MannWhitney_func(X1, T1)$tau))
})

mean(unlist(sim[1, ]))
mean(unlist(sim[2, ]))
mean(unlist(sim[3, ]))
```

#### Wilcoxon rank-sum test:
```{r}
B <- 2000
size <- 500

set.seed(20200706)
MW.sim1 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T1 <- rweibull(n = size, shape = 2, scale = 1.22)
  MW <- MannWhitney_func(X1, T1)
  
  return(list(z = MW$z,
              tau = MW$tau))
})

mean(abs(unlist(MW.sim1[1, ])) > qnorm(0.975))
mean(unlist(MW.sim1[2, ]))
```

```{r}
hist(unlist(MW.sim1[1, ]), freq = FALSE)
curve(dnorm(x), from = -3, to = 3, add = TRUE)
```

**Crossing case** <br>
```{r}
B <- 2000
size <- 500

set.seed(20200706)
MW.sim2 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 2, scale = 1.22)
  T12 <- rweibull(n = size, shape = 0.5, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  MW <- MannWhitney_func(X1, T1)
  
  return(list(z = MW$z,
              tau = MW$tau))
})

mean(abs(unlist(MW.sim2[1, ])) > qnorm(0.975))
sd(abs(unlist(MW.sim2[1, ])) > qnorm(0.975))

```

```{r}
hist(unlist(MW.sim2[1, ]), freq = FALSE)
curve(dnorm(x), from = -3, to = 3, add = TRUE)
```

**General Alternative Hypothesis** <br>
```{r}
B <- 2000
size <- 500

set.seed(20200706)
MW.sim3 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 1, scale = 4)
  T12 <- rweibull(n = size, shape = 1, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  MW <- MannWhitney_func(X1, T1)
  
  return(list(z = MW$z,
              tau = MW$tau))
})

mean(abs(unlist(MW.sim3[1, ])) > qnorm(0.975))
sd(abs(unlist(MW.sim3[1, ])) > qnorm(0.975))
```

```{r}
hist(unlist(MW.sim3[1, ]), freq = FALSE)
curve(dnorm(x), from = -3, to = 3, add = TRUE)
```

#### Gehan test:
The case that two samples are i.i.d with light censoring.
```{r}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
Gehan.sim1 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T1 <- rweibull(n = size, shape = 2, scale = 1.22)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  gehan <- Gehan_func(Y1, delta, X1)
  MW <- MannWhitney_func(X1, T1)
  
  return(list(gehan$z,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0]),
              MW$z))
})

mean(abs(unlist(Gehan.sim1[1, ])) > qnorm(0.975))
sd(abs(unlist(Gehan.sim1[1, ])) > qnorm(0.975))
mean(abs(unlist(Gehan.sim1[4, ])) > qnorm(0.975))

mean(unlist(Gehan.sim1[2, ]))
mean(unlist(Gehan.sim1[3, ]))
```

```{r}
par(mfrow = c(1, 2))
hist(unlist(Gehan.sim1[1, ]), freq = FALSE, main = "Gehan")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)

hist(unlist(Gehan.sim1[4, ]), freq = FALSE, main = "Mann-Whitney")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)
```

The case that two samples are i.i.d with heavy censoring.
```{r}
B <- 2000
size <- 500
C.rate <- 0.7

set.seed(20200706)
Gehan.sim2 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T1 <- rweibull(n = size, shape = 2, scale = 1.22)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  gehan <- Gehan_func(Y1, delta, X1)
  MW <- MannWhitney_func(X1, T1)
  
  return(list(gehan$z,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0]),
              MW$z))
})

mean(abs(unlist(Gehan.sim2[1, ])) > qnorm(0.975))
sd(abs(unlist(Gehan.sim2[1, ])) > qnorm(0.975))
mean(abs(unlist(Gehan.sim2[4, ])) > qnorm(0.975))

mean(unlist(Gehan.sim2[2, ]))
mean(unlist(Gehan.sim2[3, ]))
```

```{r}
par(mfrow = c(1, 2))
hist(unlist(Gehan.sim2[1, ]), freq = FALSE, main = "Gehan")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)

hist(unlist(Gehan.sim2[4, ]), freq = FALSE, main = "Mann-Whitney")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)
```


**Crossing case with light censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
Gehan.sim3 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 2, scale = 1.22)
  T12 <- rweibull(n = size, shape = 0.5, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  gehan <- Gehan_func(Y1, delta, X1)
  MW <- MannWhitney_func(X1, T1)
  
  return(list(gehan$z,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0]),
              MW$z))
})

mean(abs(unlist(Gehan.sim3[1, ])) > qnorm(0.975))
sd(abs(unlist(Gehan.sim3[1, ])) > qnorm(0.975))
mean(abs(unlist(Gehan.sim3[4, ])) > qnorm(0.975))

mean(unlist(Gehan.sim3[2, ]))
mean(unlist(Gehan.sim3[3, ]))
```


```{r}
par(mfrow = c(1, 2))
hist(unlist(Gehan.sim3[1, ]), freq = FALSE, main = "Gehan")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)

hist(unlist(Gehan.sim3[4, ]), freq = FALSE, main = "Mann-Whitney")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)
```

**Crossing case with heavy censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 0.7

set.seed(20200706)
Gehan.sim4 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 2, scale = 1.22)
  T12 <- rweibull(n = size, shape = 0.5, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  gehan <- Gehan_func(Y1, delta, X1)
  MW <- MannWhitney_func(X1, T1)
  
  return(list(gehan$z,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0]),
              MW$z,
              survdiff(Surv(Y1, delta) ~ X1, rho = 1)$chisq))
})

mean(abs(unlist(Gehan.sim4[1, ])) > qnorm(0.975))
sd(abs(unlist(Gehan.sim4[1, ])) > qnorm(0.975))
mean(abs(unlist(Gehan.sim4[4, ])) > qnorm(0.975))
mean(abs(unlist(Gehan.sim4[5, ])) > qchisq(0.95, df = 1))

mean(unlist(Gehan.sim4[2, ]))
mean(unlist(Gehan.sim4[3, ]))
```

```{r}
par(mfrow = c(1, 3))
hist(unlist(Gehan.sim4[1, ]), freq = FALSE, main = "Gehan")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)

hist(unlist(Gehan.sim4[4, ]), freq = FALSE, main = "Mann-Whitney")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)

hist(unlist(Gehan.sim4[5, ]), freq = FALSE, main = "Gehan2")
curve(dchisq(x, df = 1), from = 0, to = 50, lty = 2, add = TRUE)
```

**General Alternative Hypothesis** <br>
**Crossing case with light censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
Gehan.sim5 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 1, scale = 4)
  T12 <- rweibull(n = size, shape = 1, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  gehan <- Gehan_func(Y1, delta, X1)
  MW <- MannWhitney_func(X1, T1)
  
  return(list(gehan$z,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0]),
              MW$z))
})

mean(abs(unlist(Gehan.sim5[1, ])) > qnorm(0.975))
sd(abs(unlist(Gehan.sim5[1, ])) > qnorm(0.975))
mean(abs(unlist(Gehan.sim5[4, ])) > qnorm(0.975))

mean(unlist(Gehan.sim5[2, ]))
mean(unlist(Gehan.sim5[3, ]))
```

```{r}
par(mfrow = c(1, 2))
hist(unlist(Gehan.sim5[1, ]), freq = FALSE, main = "Gehan")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)

hist(unlist(Gehan.sim5[4, ]), freq = FALSE, main = "Mann-Whitney")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)
```

**Crossing case with heavy censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 0.5

set.seed(20200706)
Gehan.sim6 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 1, scale = 4)
  T12 <- rweibull(n = size, shape = 1, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  gehan <- Gehan_func(Y1, delta, X1)
  MW <- MannWhitney_func(X1, T1)
  
  return(list(gehan$z,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0]),
              MW$z))
})

mean(abs(unlist(Gehan.sim6[1, ])) > qnorm(0.975))
sd(abs(unlist(Gehan.sim6[1, ])) > qnorm(0.975))
mean(abs(unlist(Gehan.sim6[4, ])) > qnorm(0.975))

mean(unlist(Gehan.sim6[2, ]))
mean(unlist(Gehan.sim6[3, ]))
```

```{r}
par(mfrow = c(1, 2))
hist(unlist(Gehan.sim6[1, ]), freq = FALSE, main = "Gehan")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)

hist(unlist(Gehan.sim6[4, ]), freq = FALSE, main = "Mann-Whitney")
curve(dnorm(x), from = -5, to = 5, lty = 2, add = TRUE)
```


#### log-rank test:
**The case that two samples are i.i.d with light censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
logrank.sim1 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T1 <- rweibull(n = size, shape = 2, scale = 1.22)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  logrank <- logrank_func(Y1, delta, X1)
  
  return(list(logrank,
              survdiff(Surv(Y1, delta) ~ X1)$chisq,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0])))
})

mean(abs(unlist(logrank.sim1[1, ])) > qnorm(0.975))
sd(abs(unlist(logrank.sim1[1, ])) > qnorm(0.975))
mean(abs(unlist(logrank.sim1[2, ])) > qchisq(0.95, df = 1))
mean(unlist(logrank.sim1[3, ]))
mean(unlist(logrank.sim1[4, ]))
```

```{r}
hist(unlist(logrank.sim1[1, ]), freq = FALSE, main = "log-rank")
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**The case that two samples are i.i.d with heavy censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 0.7

set.seed(20200706)
logrank.sim2 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T1 <- rweibull(n = size, shape = 2, scale = 1.22)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  logrank <- logrank_func(Y1, delta, X1)
  
  return(list(logrank,
              survdiff(Surv(Y1, delta) ~ X1)$chisq,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0])))
})

mean(abs(unlist(logrank.sim2[1, ])) > qnorm(0.975))
sd(abs(unlist(logrank.sim2[1, ])) > qnorm(0.975))
mean(abs(unlist(logrank.sim2[2, ])) > qchisq(0.95, df = 1))
mean(unlist(logrank.sim2[3, ]))
mean(unlist(logrank.sim2[4, ]))
```

```{r}
hist(unlist(logrank.sim2[1, ]), freq = FALSE, main = "log-rank")
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**Crossing case with light censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
logrank.sim3 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 2, scale = 1.22)
  T12 <- rweibull(n = size, shape = 0.5, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  logrank <- logrank_func(Y1, delta, X1)
  
  return(list(logrank,
              survdiff(Surv(Y1, delta) ~ X1)$chisq,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0])))
})

mean(abs(unlist(logrank.sim3[1, ])) > qnorm(0.975))
sd(abs(unlist(logrank.sim3[1, ])) > qnorm(0.975))
mean(abs(unlist(logrank.sim3[2, ])) > qchisq(0.95, df = 1))
mean(unlist(logrank.sim3[3, ]))
mean(unlist(logrank.sim3[4, ]))
```

```{r}
hist(unlist(logrank.sim3[1, ]), freq = FALSE, main = "log-rank")
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**Crossing case with heavy censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 0.7

set.seed(20200706)
logrank.sim4 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 2, scale = 1.22)
  T12 <- rweibull(n = size, shape = 0.5, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  logrank <- logrank_func(Y1, delta, X1)
  
  return(list(logrank,
              survdiff(Surv(Y1, delta) ~ X1)$chisq,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0])))
})

mean(abs(unlist(logrank.sim4[1, ])) > qnorm(0.975))
sd(abs(unlist(logrank.sim4[1, ])) > qnorm(0.975))
mean(abs(unlist(logrank.sim4[2, ])) > qchisq(0.95, df = 1))
mean(unlist(logrank.sim4[3, ]))
mean(unlist(logrank.sim4[4, ]))
```

```{r}
hist(unlist(logrank.sim4[1, ]), freq = FALSE, main = "log-rank")
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**General Alternative Hypothesis** <br>
**Crossing case with light censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
logrank.sim5 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 1, scale = 4)
  T12 <- rweibull(n = size, shape = 1, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  logrank <- logrank_func(Y1, delta, X1)
  
  return(list(logrank,
              survdiff(Surv(Y1, delta) ~ X1)$chisq,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0])))
})

mean(abs(unlist(logrank.sim5[1, ])) > qnorm(0.975))
sd(abs(unlist(logrank.sim5[1, ])) > qnorm(0.975))
mean(abs(unlist(logrank.sim5[2, ])) > qchisq(0.95, df = 1))
mean(unlist(logrank.sim5[3, ]))
mean(unlist(logrank.sim5[4, ]))
```

```{r}
hist(unlist(logrank.sim5[1, ]), freq = FALSE, main = "log-rank")
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**Crossing case with light censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 0.5

set.seed(20200706)
logrank.sim6 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 1, scale = 4)
  T12 <- rweibull(n = size, shape = 1, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  logrank <- logrank_func(Y1, delta, X1)
  
  return(list(logrank,
              survdiff(Surv(Y1, delta) ~ X1)$chisq,
              mean(delta[X1 == 1]),
              mean(delta[X1 == 0])))
})

mean(abs(unlist(logrank.sim6[1, ])) > qnorm(0.975))
sd(abs(unlist(logrank.sim6[1, ])) > qnorm(0.975))
mean(abs(unlist(logrank.sim6[2, ])) > qchisq(0.95, df = 1))
mean(unlist(logrank.sim6[3, ]))
mean(unlist(logrank.sim6[4, ]))
```

```{r}
hist(unlist(logrank.sim6[1, ]), freq = FALSE, main = "log-rank")
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

#### proposed test (IPCW):
**The case that two samples are i.i.d with light censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
IPCW.sim1 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T1 <- rweibull(n = size, shape = 2, scale = 1.22)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  
  tau.hat <- ipcw_binary_tau(Y1, delta, X1, T1)
  
  return(tau.hat)
})

mean(abs(IPCW.sim1 / sd(IPCW.sim1)) > qnorm(0.975))
sd(abs(IPCW.sim1 / sd(IPCW.sim1)) > qnorm(0.975))
```

```{r}
hist(IPCW.sim1 / sd(IPCW.sim1), freq = FALSE)
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**The case that two samples are i.i.d with heavy censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 0.7

set.seed(20200706)
IPCW.sim2 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T1 <- rweibull(n = size, shape = 2, scale = 1.22)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  
  tau.hat <- ipcw_binary_tau(Y1, delta, X1, T1)
  
  return(tau.hat)
})

mean(abs(IPCW.sim2 / sd(IPCW.sim2)) > qnorm(0.975))
sd(abs(IPCW.sim2 / sd(IPCW.sim2)) > qnorm(0.975))
```

```{r}
hist(IPCW.sim2 / sd(IPCW.sim1), freq = FALSE)
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**Crossing case with light censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
IPCW.sim3 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 2, scale = 1.22)
  T12 <- rweibull(n = size, shape = 0.5, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  
  tau.hat <- ipcw_binary_tau(Y1, delta, X1, T1)
  
  return(tau.hat)
})

mean(abs(IPCW.sim3 / sd(IPCW.sim3)) > qnorm(0.975))
sd(abs(IPCW.sim3 / sd(IPCW.sim3)) > qnorm(0.975))
```

```{r}
hist(IPCW.sim3 / sd(IPCW.sim3), freq = FALSE)
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**Crossing case with heavy censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 0.7

set.seed(20200706)
IPCW.sim4 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 2, scale = 1.22)
  T12 <- rweibull(n = size, shape = 0.5, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  
  tau.hat <- ipcw_binary_tau(Y1, delta, X1, T1)
  
  return(tau.hat)
})

mean(abs(IPCW.sim4 / sd(IPCW.sim4)) > qnorm(0.975))
sd(abs(IPCW.sim4 / sd(IPCW.sim4)) > qnorm(0.975))
```

```{r}
hist(IPCW.sim4 / sd(IPCW.sim4), freq = FALSE)
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**General Alternative Hypothesis** <br>
**Crossing case with light censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
IPCW.sim5 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 1, scale = 4)
  T12 <- rweibull(n = size, shape = 1, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  
  tau.hat <- ipcw_binary_tau(Y1, delta, X1, T1)
  
  return(tau.hat)
})

mean(abs(IPCW.sim5 / sd(IPCW.sim5)) > qnorm(0.975))
sd(abs(IPCW.sim5 / sd(IPCW.sim5)) > qnorm(0.975))
```

```{r}
hist(IPCW.sim5 / sd(IPCW.sim5), freq = FALSE)
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

**Crossing case with heavy censoring** <br>
```{r}
B <- 2000
size <- 500
C.rate <- 0.5

set.seed(20200706)
IPCW.sim6 <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 1, scale = 4)
  T12 <- rweibull(n = size, shape = 1, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  
  tau.hat <- ipcw_binary_tau(Y1, delta, X1, T1)
  
  return(tau.hat)
})

mean(abs(IPCW.sim6 / sd(IPCW.sim6)) > qnorm(0.975))
sd(abs(IPCW.sim6 / sd(IPCW.sim6)) > qnorm(0.975))
```

```{r}
hist(IPCW.sim6 / sd(IPCW.sim6), freq = FALSE)
curve(dnorm(x), from = -3, to = 3, lty = 2, add = TRUE)
```

#### K-S test:
```{r warning=FALSE}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
ks.sim <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T1 <- rweibull(n = size, shape = 2, scale = 1.22)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  
  return(ks.test(x = T1[X1 == 1], y = T1[X1 == 0], alternative = "two.sided")$p.value)
})

mean(ks.sim < 0.05)
sd(ks.sim < 0.05)
```

```{r warning=FALSE}
B <- 2000
size <- 500
C.rate <- 1e-5

set.seed(20200706)
ks.sim <- replicate(n = B, expr = {
  X1 <- rbinom(n = size, size = 1, prob = 0.5)
  T11 <- rweibull(n = size, shape = 2, scale = 1.22)
  T12 <- rweibull(n = size, shape = 0.5, scale = 2)
  T1 <- ifelse(X1 == 1, T11, T12)
  C <- rexp(n = size, rate = C.rate)
  Y1 <- ifelse(T1 < C, T1, C)
  delta <- ifelse(T1 < C, 1, 0)
  
  return(ks.test(x = T11, y = T12, alternative = "two.sided")$p.value)
})

mean(ks.sim < 0.05)
sd(ks.sim < 0.05)
```
